---
title: "Lipids Audit"
author: "Rob Willans"
date: "15/03/2022"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)

knitr::opts_chunk$set(echo = TRUE)


## Load data from cohort extractor
df_input <- read_csv(here::here("output", "input.csv")) %>%
  mutate(
    "age_group" = case_when(
      age < 40 ~ "18-39",
      age < 60 ~ "40-59",
      age < 80 ~ "60-79",
      age >= 80 ~ "80-84",
      TRUE ~ "No age"
    ),
    "CVD_assess_cat" = case_when(
      is.na(CVD_assess_latest_number) ~ "No CVD Risk Assessment Noted",
      TRUE ~ "CVD Risk Assessment"
    ),
    "statin_cat" = case_when(
      is.na(statins_prescribed) ~ "No Statin Recorded",
      TRUE ~ "Statins Recorded"
    ),
    "cvd_statin_cat" = case_when(
      is.na(cvdprevent_statins_prescribed) ~ "No Statin Recorded (CVDPREVENT)",
      TRUE ~ "Statins Recorded (CVDPREVENT)"
    )
  )
  

summarise_df_by_group <- function(df, ...){
  df %>% 
    group_by(...) %>% 
    summarise(n=n()) %>% 
    ungroup() %>% 
    mutate("percentage" = n/sum(n)*100) %>%
    adorn_totals()
  }

```

# Initial counts

## Total N (aged 18-84 inclusive at end of 2021)

```{r}

nrow(df_input)

```



## N with CVD diagnosis 

```{r CVD_n}

df_input %>%
  filter(CVD_code == 1) %>% 
  summarise_df_by_group(age_group)

```

## N with CKD diagnosis 

```{r CKD_n}

df_input %>%
  filter(CKD_code == 1) %>% 
  summarise_df_by_group(age_group)

```

## N with T1D diagnosis

```{r T1D_n}

df_input %>%
  filter(T1D_code == 1) %>% 
  summarise_df_by_group(age_group)

```

## N with T2D diagnosis

```{r T2D_n}

df_input %>%
  filter(T2D_code == 1) %>% 
  summarise_df_by_group(age_group)

```

## N with any DM diagnosis

```{r anyDcode_n}

df_input %>%
  filter(Overall_diab_code == 1) %>% 
  summarise_df_by_group(age_group)

```
## N total statin prescriptions

```{r totalstatins}

df_input %>% 
  summarise_df_by_group(statin_cat)

```

## N total statin prescriptions (CVDPREVENT statin list)

```{r totalstatinscvdp}

df_input %>% 
  summarise_df_by_group(cvd_statin_cat)

```

## Calculate % patients with CVD assessment at any time

```{r addCVDriskcat}

df_input %>% 
  summarise_df_by_group(sex, age_group, CVD_assess_cat)
         
```


# Calculations

## N excluding CVD, CKD, T1D (aged 40-84 at 2022-01-01)

```{r noCVDCKDT1D}

df_input %>% 
  filter(age >= 40,
         CVD_code == 0,
         CKD_code == 0, 
         T1D_code == 0) %>% 
  nrow()

```

## N excluding CVD, CKD, T1D and risk assessment more than 5 years ago

•	How many people aged 40-84y (excluding pre-existing CVD, T1DM and CKD) have had a CVD risk assessment recorded in the preceding 5 years?

```{r excluderiskassessmorethanfiveyears}

df_input %>% 
  filter(age >= 40,
         CVD_code == 0,
         CKD_code == 0, 
         T1D_code == 0,
         CVD_assess_latest_date >= "2016-12-31") %>% 
  nrow()

```

## Calculate % patients (by age group) with CVD risk over 10 with statin prescription

```{r CVDgreaterthan10statins}

df_input %>% 
  filter(CVD_assess_latest_number >= 10) %>% 
  summarise_df_by_group(age_group, statin_cat) 


```

## Calculate % patients (by age group) with CVD risk over 10 with statin prescription [Alternate CVDPreventStatinsList]

```{r CVDgreaterthan10statinsalt}

df_input %>% 
  filter(CVD_assess_latest_number >= 10) %>% 
  summarise_df_by_group(age_group, cvd_statin_cat) 


```

## Calculate % patients with CVD risk over 20 with statin prescription 

```{r CVDgreaterthan20statins}

df_input %>% 
  filter(CVD_assess_latest_number >= 20) %>% 
  summarise_df_by_group(sex, age_group, statin_cat) 

```

## Calculate % patients with CVD risk over 20 with statin prescription [Alternate CVDPreventStatinsList]

```{r CVDgreaterthan20statinsalt}

df_input %>% 
  filter(CVD_assess_latest_number >= 20) %>% 
  summarise_df_by_group(sex, age_group, cvd_statin_cat) 

```


## Calculate % patients (age group) with prior CVD diag (on or before 2021-12-31) and statin prescription (on or before 2021-12-31)

```{r CVD }

df_input %>% 
  filter(CVD_code == 1) %>% 
  summarise_df_by_group(age_group, statin_cat, cvd_statin_cat) 

```

## Calculate % patients (age group) with prior CKD diag (on or before 2021-12-31) and statin prescription (on or before 2021-12-31)

```{r preexistCKDgtatins}

df_input %>% 
  filter(CKD_code == 1) %>% 
  summarise_df_by_group(age_group, statin_cat, cvd_statin_cat) 


```

