---
title: "Lipids Audit"
author: "Rob Willans"
date: "15/03/2022"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)

knitr::opts_chunk$set(echo = TRUE)


## Load data from cohort extractor
df_input <- read_csv(
  here::here("output", "input.csv")
  ) %>% 
  mutate(age_group = case_when(age >= 40 ~ "40+",
                               age < 40 ~ "Under 40",
                               TRUE ~ "No age"))

summarise_df_by_age_group <- function(df){
  df %>% 
    group_by(age_group) %>% 
    summarise(n=n())
}

```

## Total N

```{r}

nrow(df_input)

```

## Number of patients with CVD

```{r CVD_n}

df_cvd <- df_input %>%
  filter(CVD_code == 1)


df_cvd %>% 
  summarise_df_by_age_group()

```

## Number of patients with CKD

```{r CKD_n}

df_ckd <- df_input %>%
  filter(CKD_code == 1)

df_ckd %>% 
  summarise_df_by_age_group()

```


## N after excluding people with CVD, CKD, T1D

```{r noCVDCKDT1D}

df_no_comorbs_over40 <- df_input %>% 
  filter(age >= 40,
         CVD_code == 0,
         CKD_code == 0, 
         T1D_code == 0)

nrow(df_no_comorbs_over40)

```
## N after excluding patients with risk assessment more than 5 years ago

```{r excluderiskassessmorethanfiveyears}

df_input_2 <- df_input %>% 
  filter(age >= 40,
         CVD_code == 0,
         CKD_code == 0, 
         T1D_code == 0,
         CVD_assess_latest_date >= "2017-01-01")

```

## calculate % patients with CVD assessment in past 5 years

```{r addCVDriskcat}

df_input_2 <- df_input_2 %>% 
  mutate("CVD_assess_cat" = case_when(is.na(CVD_assess_latest_number) ~ "No CVD Risk Assessment Noted",
                                      TRUE ~ "CVD Risk Assessment"))

df_input_2 %>% 
  group_by(CVD_assess_cat) %>% 
  summarise(n = n(), Percentage = n/nrow(df_input_2)*100, .groups = "keep") %>% 
  ungroup()
         
```

## calculate % patients with CVD risk over 10 on statins

```{r CVDgreaterthan10statins}

data_risk10 <- df_input_2 %>% 
  filter(CVD_assess_latest_number >= 10) %>% 
  mutate("statin_cat" = case_when(is.na(statins_prescribed) ~ "No Statin Recorded",
                                  TRUE ~ "Statins Recorded"))

data_risk10 %>% 
  group_by(statin_cat) %>% 
  summarise(n = n(), percentage = n/nrow(data_risk10))

```

## calculate % patients with CVD risk over 20 on statins

```{r CVDgreaterthan20statins}

data_risk20 <- df_input_2 %>% 
  filter(CVD_assess_latest_number >= 20) %>% 
  mutate("statin_cat" = case_when(is.na(statins_prescribed) ~ "No Statin Recorded",
                                  TRUE ~ "Statins Recorded"))

data_risk20 %>% 
  group_by(statin_cat) %>% 
  summarise(n = n(), percentage = n/nrow(data_risk20))

```


## calculate % patients with pre-existing CVD on statins

```{r preexistCVDgtatins}

df_cvd <- df_cvd %>% 
  mutate("statin_cat" = case_when(is.na(statins_prescribed) ~ "No Statin Recorded",
                                  TRUE ~ "Statins Recorded"))

df_cvd %>% 
  group_by(statin_cat) %>% 
  summarise(n = n(), percentage = n/nrow(df_cvd))

```

## calculate % patients with CKD on statins

```{r preexistCKDgtatins}

df_ckd <- df_ckd %>% 
  mutate("statin_cat" = case_when(is.na(statins_prescribed) ~ "No Statin Recorded",
                                  TRUE ~ "Statins Recorded"))

df_ckd %>% 
  group_by(statin_cat) %>% 
  summarise(n = n(), percentage = n/nrow(df_ckd))

```