---
title: "Lipids Audit"
author: "Rob Willans"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}

library(tidyverse)
library(janitor)

knitr::opts_chunk$set(echo = TRUE)

## Load data from cohort extractor
df_input <- read_csv(here::here("output", "input.csv")) %>%
  mutate(
    "age_group" = case_when(
      age < 60 ~ "40-59",
      age < 80 ~ "60-79",
      age >= 80 ~ "80-84",
      TRUE ~ "No age"
    ),
    "CVD_assess_cat" = case_when(
      CVD_assess_latest_number > 0 ~ "CVD risk assessment",
      (is.na(CVD_assess_latest_number)|CVD_assess_latest_number == 0) ~ "No CVD risk assessment number",
      TRUE ~ "Negative or Invalid Input"
    ),
    "cvd_statin_cat_last_6m" = case_when(
      is.na(cvdprevent_statins_issued_last_6m) ~ "No statin recorded in last 6m",
      TRUE ~ "Statins recorded in last 6m"
    ),
    "lipid_modifier_last_6_primary" = case_when(
      is.na(lipid_modifier_primary) ~ "No lipid modifier recorded in last 6m",
      TRUE ~ "Lipid modifier recorded in last 6m"
    ),
    "lipid_modifier_last_6_secondary" = case_when(
      is.na(lipid_modifier_secondary) ~ "No lipid modifier recorded in last 6m",
      TRUE ~ "Lipid modifier recorded in last 6m"
    )
  )

summarise_df_by_group <- function(df, ...){
  df %>% 
    group_by(...) %>% 
    summarise(n=n()) %>% 
    ungroup() %>% 
    mutate("percentage" = sprintf("%.2f%%", n/sum(n)*100)) %>%
    adorn_totals()
  }

filter_for_40_84_assess_in_last_five_years_no_CVD_CKD_T1D <- function(df){
  
df %>% 
  filter(CVD_code_CVD_prevent == 0,
         CKD_code == 0, 
         T1D_code == 0,
         CVD_assess_latest_date >= "2016-12-31",
         CVD_assess_latest_date <= "2021-12-31")

}  
  
```

# Initial counts

## Total N (aged 40-84 inclusive at end of 2021)

```{r}

nrow(df_input)

```

## N with CVD diagnosis 

* CVD codelist taken from CVDPrevent definitions, including stroke codes,  TIA codes, CHD codes, PAD codes and excluding HF and AAA codes

```{r CVD_n}

df_input %>%
  filter(CVD_code_CVD_prevent == 1) %>% 
  summarise_df_by_group(age_group)

```

## N with CKD diagnosis 

```{r CKD_n}

df_input %>%
  filter(CKD_code == 1) %>% 
  summarise_df_by_group(age_group)

```

## N with T1D diagnosis

```{r T1D_n}

df_input %>%
  filter(T1D_code == 1) %>% 
  summarise_df_by_group(age_group)

```

## N total statin issues in last 6m

```{r totalstatinscvdp6m}

df_input %>% 
  summarise_df_by_group(cvd_statin_cat_last_6m)

```
## N total lipid modifier issues in last 6m

```{r totallipids6m}

df_input %>% 
  summarise_df_by_group(lipid_modifier_last_6_primary)

df_input %>% 
  summarise_df_by_group(lipid_modifier_last_6_secondary)


```


## N excluding CVD, CKD, T1D  who have had risk assessment in last 5 years who are aged 40-84 inclusive [Indicator 1 Numerator]

•	How many people aged 40-84y (excluding pre-existing CVD, T1DM and CKD) have had a CVD risk assessment recorded in the preceding 5 years?

```{r excluderiskassessmorethanfiveyears}

df_input %>% 
  filter_for_40_84_assess_in_last_five_years_no_CVD_CKD_T1D() %>% 
  nrow()

```
## N excluding CVD, CKD, T1D who are aged 40-84 inclusive [Indicator 1 Denominator]

```{r noCVDCKDT1D}

df_input %>% 
  filter(age >= 40,
         CVD_code_CVD_prevent == 0,
         CKD_code == 0, 
         T1D_code == 0) %>% 
  nrow()


```

# Calculations - statins only

## Calculate % patients (by age group) with CVD risk over 10 with statin issue in last 6m

3.	How many people with a recorded CVD risk assessment score of ≥ 10% in last 5 years are currently treated (defined as issue in last 6m) with a statin. 

```{r CVDgreaterthan10statins}

df_input %>% 
  filter_for_40_84_assess_in_last_five_years_no_CVD_CKD_T1D() %>% 
  filter(CVD_assess_latest_number >= 10) %>% 
  summarise_df_by_group(cvd_statin_cat_last_6m) 

```

```{r CVDgreaterthan10statinsage}

df_input %>% 
  filter_for_40_84_assess_in_last_five_years_no_CVD_CKD_T1D() %>% 
  filter(CVD_assess_latest_number >= 10)%>% 
  summarise_df_by_group(cvd_statin_cat_last_6m, age_group) 

```

## Calculate % patients with CVD risk over 20 with statin issue in last 6m

4.	How many people with a recorded CVD risk assessment score of ≥ 20% in last 5 years are currently treated (defined as issue within last 6m) with a statin. 

```{r CVDgreaterthan20statinsalt}

df_input %>% 
  filter_for_40_84_assess_in_last_five_years_no_CVD_CKD_T1D() %>% 
  filter(CVD_assess_latest_number >= 20) %>% 
  summarise_df_by_group(cvd_statin_cat_last_6m) 

```

```{r CVDgreaterthan20statinsaltage}

df_input %>% 
  filter_for_40_84_assess_in_last_five_years_no_CVD_CKD_T1D() %>% 
  filter(CVD_assess_latest_number >= 20) %>% 
  summarise_df_by_group(cvd_statin_cat_last_6m, age_group) 

```

## Calculate % patients with pre-existing CVD/CKD currently treated with a statin.

5.	How many people with pre-existing CVD or CKD are currently treated (defined as issue within last 6 months) with a statin.

```{r CVDCKDstatins6m}

df_input %>% 
  filter(age >= 40,
         CVD_assess_latest_date >= "2016-12-31",
         CVD_assess_latest_date <= "2021-12-31",
         CVD_code_CVD_prevent == 1 | CKD_code == 1) %>% 
  summarise_df_by_group(cvd_statin_cat_last_6m) 

```
# Calculations - statins plus non-statin lipid modifiers

## Calculate % patients (by age group) with CVD risk over 10 with lipid modifying therapy issue in last 6m

3.	How many people with a recorded CVD risk assessment score of ≥ 10% in last 5 years are currently treated (defined as issue in last 6m) with lipid modifying therapy. 

```{r CVDgreaterthan10lipids}

df_input %>% 
  filter_for_40_84_assess_in_last_five_years_no_CVD_CKD_T1D() %>% 
  filter(CVD_assess_latest_number >= 10) %>% 
  summarise_df_by_group(lipid_modifier_last_6_primary) 

```

```{r CVDgreaterthan10lipidsage}

df_input %>% 
  filter_for_40_84_assess_in_last_five_years_no_CVD_CKD_T1D() %>% 
  filter(CVD_assess_latest_number >= 10)%>% 
  summarise_df_by_group(lipid_modifier_last_6_primary, age_group) 

```

## Calculate % patients with CVD risk over 20 with lipid modifying therapy issue in last 6m

4.	How many people with a recorded CVD risk assessment score of ≥ 20% in last 5 years are currently treated (defined as issue within last 6m) with lipid modifying therapy. 

```{r CVDgreaterthan20lipidsalt}

df_input %>% 
  filter_for_40_84_assess_in_last_five_years_no_CVD_CKD_T1D() %>% 
  filter(CVD_assess_latest_number >= 20) %>% 
  summarise_df_by_group(lipid_modifier_last_6_primary) 

```

```{r CVDgreaterthan20lipidsaltage}

df_input %>% 
  filter_for_40_84_assess_in_last_five_years_no_CVD_CKD_T1D() %>% 
  filter(CVD_assess_latest_number >= 20) %>% 
  summarise_df_by_group(lipid_modifier_last_6_primary, age_group) 

```

## Calculate % patients with pre-existing CVD/CKD currently treated with a statin.

5.	How many people with pre-existing CVD or CKD are currently treated (defined as issue within last 6 months) with lipid modifying therapy.

```{r CVDCKDlipidmod6m}

df_input %>% 
  filter(age >= 40,
         CVD_assess_latest_date >= "2016-12-31",
         CVD_assess_latest_date <= "2021-12-31",
         CVD_code_CVD_prevent == 1 | CKD_code == 1) %>% 
  summarise_df_by_group(lipid_modifier_last_6_secondary) 

```
